\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-27 paper.tex
More on clients + various little bits

\section{Design and Architecture}

@@

Every node has a unique ID, a parent, a 3D transformation relative to the parent
and an optional name. \emph{Object} nodes optionally store as well pointers to their
associated meshes.

@@

\paragraph{Assets loading}

{\tt uwds load}

@@

\subsection{Spatial Reasoning}

Spatial reasoning~\cite{O'Keefe1999} is a field in its own right, and has been
used for natural language processing for applications such as direction
recognition ~\cite{Kollar2010,Matuszek2010} or language
grounding~\cite{Tellex2010}.~\cite{Skubic2004} present a spatial reasoner
integrated in a robot which computes symbolic positions of objects.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{spatialrelations}
    \caption{The {\tt spatial\_relations} client computes perspective-aware
    spatial relations between objects and agents}
    \label{fig|spatialrelations}
\end{figure}

\cite{Ros2010}

\subsubsection{Visibility computation}

{\tt uwds visibility}

\subsubsection{Perspective Taking}

@@

\end{pythoncode}
    \caption{This \uwds client creates a world named {\tt human\_perspective}
    from a source world {\tt base} by only updating objects that are in the
    human field of view. As such, {\tt human\_perspective} is a real-time model
    of the human perspective on the scene.}

@@

\section{Conclusion}

@@

Interplay with effort like RSG-DSL~\cite{blumenthal2014towards}

@@

>>>>

The main contribution of this work is a generic approach to represent and share
\textbf{multiple parallel representations of the world}. \uwds does so by
permitting clients to clone an existing world, modify it, and re-share it,
without the cost of duplicating geometric data (as explained in
section~\ref{design}). By organizing clients in a network
(Figure~\ref{fig|scene}), worlds can be made dependent on each other, resulting
in a loosely-coupled modular approach to spatio-temporal world representation
that we call \emph{cascading situation assessment}.

\section{Design and Architecture}
\label{design}

@@

Every node has a unique ID, a parent, a 3D transformation relative to the parent
and an optional name. \emph{Object} nodes optionally store as well pointers to their
associated meshes. Importantly, mesh data (or other geometric datasets like
point clouds) are \emph{not} stored within the nodes. \uwds represents geometric
data as immutable data, labelled with their hash (preventing data duplication).
Nodes only store the hash of their geometric data, and the actual data is pulled
by client whenever they actually need it (for rendering for instance).

@@

\paragraph*{Assets loading}

Geometric data like meshes can be loaded into a world (or rather, into the whole
network as geometric data are treated as immutable resources shared amongst all
worlds) by simply sending an array of vertices and faces to the \uwds server.
As such, any client can load 3D data that is automatically made available to the
whole network. For example, an object recognition module recognizes a new
object. It sends the mesh to the \uwds server and creates a new node which
references the mesh. At the next frame update, the 3D viewer sees a new node
referencing a yet unknown mesh. The viewer request the mesh data from the
server, stores it internally (\eg as an OpenGL buffer), and renders it. Whenever
the node transformation is updated, the 3D viewer can re-render it without
having to download the mesh from the server again.

Often, objects manipulated by the robot have known meshes with corresponding CAD
models. In these case, \uwds provides a tool, {\tt uwds load}, that loads a mesh
into a \uwds network (and optionally, creates a node) from a large range of 3D
format\footnote{The underlying import capability is provided by the {\sc assimp}
library.  \url{http://assimp.sourceforge.net/}} (including Collada, FBX, OBJ,
Blender).

@@

\subsection{Spatial Reasoning and Perspective Taking}

Spatial reasoning~\cite{O'Keefe1999} is a field in its own right, and has been
used for natural language processing for applications such as direction
recognition~\cite{Kollar2010,Matuszek2010} or language
grounding~\cite{Tellex2010}. Other examples in human-robot interaction include Ros
\etal~\cite{ros2010solving, ros2010which} which has been recently integrated
into a full architecture for autonomous human-robot
interaction~\cite{lemaignan2016artificial}.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{spatialrelations}
    \caption{The {\tt spatial\_relations} client computes perspective-aware
    spatial relations between objects and agents: \emph{allo-centric} relations (like
    {\tt is in} or {\tt is on}) are independent of the viewpoint, while
    \emph{ego-centric} relations ({\tt in front of}, {\tt left of}) depend on
    the viewer perspective.}
    \label{fig|spatialrelations}
\end{figure}

\uwds provides a client ({\tt spatial\_relations}) to compute both
allo-centric and ego-centric (\ie viewer-dependent) spatial relations
between objects (Figure~\ref{fig|spatialrelations}).

\uwds also implement an efficient algorithm to assess object visibility from a
specific viewpoint (\ie from a given \emph{camera} node). The algorithm (color
picking) enables fast (single pass) computation of the visibility of every
object in the scene, while providing control regarding how much of an object
should be actually visible to be considered as globally visible. The
command-line tool {\tt uwds visibility} returns the list of visible objects from
the point of view of every camera in a given world, and \uwds also provides the
helper class {\tt VisibilityMonitor} to programmatically access visibility
information.

When integrated into a filter node, visibility computation enables to easily
create new worlds representing the estimated perspectives of the different
agents. Listing~\ref{lst|humanperspective} provides the complete code of such an
\uwds client.

@@

\end{pythoncode}
    \caption{Example of an \uwds client that creates a world named {\tt
    human\_perspective} from a source world {\tt base} by only updating objects
    that are in the field of view of the human. As such, {\tt human\_perspective} is
    a real-time model of the human perspective on the scene.}

@@

\section{Discussion and Conclusion}

@@

\subsection{Conclusion}

Integration with effort like RSG-DSL~\cite{blumenthal2014towards}

@@

The authors also acknowledge the contribution of the HRI lab of LAAS-CNRS (where this
work debuted), and in particular, the influential ideas of Rachid Alami.
